---
output: cynkratemplate::readme_document
---

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![rcc](https://github.com/tidyverse/blob/workflows/rcc/badge.svg)](https://github.com/tidyverse/blob/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/blob)](https://cran.r-project.org/package=blob)
[![Coverage Status](https://codecov.io/gh/tidyverse/blob/graph/badge.svg)](https://app.codecov.io/gh/tidyverse/blob/tree/main)
<!-- badges: end -->

<!-- README.md and index.md are generated from README.Rmd.
     Edit that file and render it the usual way: rmarkdown::render(), devtools::build_readme(), or the Knit button.
     The cynkratemplate package must be installed; it supplies the output format. -->

```{r, include = FALSE}
pkgload::load_all()

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

clean_output <- function(x, options) {
  x <- gsub("0x[0-9a-f]{3,}", "0xdeadbeef", x)
  x <- gsub("dataframe_[0-9]*_[0-9]*", "      dataframe_42_42      ", x)
  x <- gsub("[0-9]*\\.___row_number ASC", "42.___row_number ASC", x)

  x
}

options(
  cli.num_colors = 256,
  cli.width = 71,
  width = 71,
  pillar.bold = TRUE,
  pillar.max_title_chars = 5,
  pillar.min_title_chars = 5,
  pillar.max_footer_lines = 12,
  conflicts.policy = list(warn = FALSE)
)

local({
  hook_source <- knitr::knit_hooks$get("document")
  knitr::knit_hooks$set(document = clean_output)
})
```

# blob

## Overview

The goal of blob is to provide a simple S3 class to represent a vector of binary objects, aka blobs.
The `blob` class is a lightweight wrapper around a list of raw vectors, suitable for inclusion in a data frame.

In most cases you will not need to use this package explicitly:
it will be used transparently by packages that need to load BLOB columns from databases or binary file formats.

## Goals and non-goals

blob aims to:

- Provide exactly one class, `blob`, built on `vctrs::list_of(raw())`,
  so that a vector of binary objects can live in a data frame column.
- Keep the constructors small and explicit:
  `new_blob()` for a list of raw vectors, `blob()` for individual ones,
  `as_blob()` for casting and `validate_blob()` for checking.
- Behave like a well-mannered vctrs vector,
  with `vec_ptype2()` and `vec_cast()` methods so that combining, subsetting and coercion follow the usual rules.
- Print each element by its size rather than its bytes,
  as `blob[12 B]` on its own and as `<raw 12 B>` in a tibble column.
- Stay cheap to depend on:
  only methods, rlang and vctrs are imported,
  and the pillar method is registered on load only if pillar is available.

It is explicitly not trying to:

- Be a package you reach for directly:
  in most cases it is used transparently by packages that load BLOB columns from databases or binary file formats.
- Produce or store the binary data itself:
  those packages hand over the raw vectors, and blob only holds them.
- Show or interpret the contents:
  formatting reports the size of each element, and nothing here decodes, parses or compresses a blob.
- Accept every input that could plausibly become bytes:
  casts exist for lists, lists of raw, raw vectors and character, and coercing an integer vector is deprecated.


## Installation

```r
# The easiest way to get blob is to install the whole tidyverse:
install.packages("tidyverse")

# Alternatively, install just blob:
install.packages("blob")

# Or the development version from GitHub:
# install.packages("pak")
pak::pak("tidyverse/blob")
```

## Example

To create a blob, use `blob()`, `new_blob()` or `as_blob()`:

```{r example}
library(blob)

x1 <- charToRaw("Good morning")
x2 <- as.raw(c(0x48, 0x65, 0x6c, 0x6c, 0x6f))

new_blob(list(x1, x2))
blob(x1, x2)

as_blob(c("Good morning", "Good evening"))

# Inside a tibble, `pillar_shaft.blob()` decides how the column looks.
tibble::tibble(x = blob(x1, x2))
```

---

Please note that the 'blob' project is released with a [Contributor Code of Conduct](https://github.com/tidyverse/blob/blob/main/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
