---
output:
  github_document:
    html_preview: false
---

[![Travis-CI Build Status](https://travis-ci.org/tidyverse/blob.svg?branch=master)](https://travis-ci.org/tidyverse/blob)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/blob)](https://cran.r-project.org/package=blob)
[![Coverage Status](https://codecov.io/gh/tidyverse/blob/branch/master/graph/badge.svg)](https://codecov.io/github/tidyverse/blob?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(blob)
```

# blob

## Overview

The goal of blob is to provide a simple S3 class to represent a vector of binary objects, aka blobs. The `blob` class is a lightweight wrapper around a list of raw vectors, suitable for inclusion in a data frame.

In most cases you will not need to use this package explicitly: it will be used transparently by packages that need to load BLOB columns from databases or binary file formats.

## Installation

You can install blob from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tidyverse/blob")
```

## Example

To create a blob, use `blob()`, `new_blob()` or `as.blob()`:

```{r example}
x1 <- charToRaw("Good morning")
x2 <- as.raw(c(0x48, 0x65, 0x6c, 0x6c, 0x6f))

new_blob(list(x1, x2))
blob(x1, x2)

as.blob(c("Good morning", "Good evening"))
```
