---
output:
  github_document:
    html_preview: false
---

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![rcc](https://github.com/tidyverse/blob/workflows/rcc/badge.svg)](https://github.com/tidyverse/blob/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/blob)](https://cran.r-project.org/package=blob)
[![Coverage Status](https://codecov.io/gh/tidyverse/blob/branch/main/graph/badge.svg)](https://app.codecov.io/gh/tidyverse/blob)
<!-- badges: end -->

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
pkgload::load_all()

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

clean_output <- function(x, options) {
  x <- gsub("0x[0-9a-f]+", "0xdeadbeef", x)
  x <- gsub("dataframe_[0-9]*_[0-9]*", "      dataframe_42_42      ", x)
  x <- gsub("[0-9]*\\.___row_number ASC", "42.___row_number ASC", x)

  index <- x
  index <- gsub("─", "-", index)
  index <- strsplit(paste(index, collapse = "\n"), "\n---\n")[[1]][[2]]
  writeLines(index, "index.md")

  x <- gsub(
    '(`vignette[(]"([^"]+)"[)]`)',
    "[\\1](https://blob.tidyverse.org/articles/\\2.html)",
    x
  )
  x <- fansi::strip_sgr(x)
  x
}

options(
  cli.num_colors = 256,
  cli.width = 71,
  width = 71,
  pillar.bold = TRUE,
  pillar.max_title_chars = 5,
  pillar.min_title_chars = 5,
  pillar.max_footer_lines = 12,
  conflicts.policy = list(warn = FALSE)
)

local({
  hook_source <- knitr::knit_hooks$get("document")
  knitr::knit_hooks$set(document = clean_output)
})
```

# blob

## Overview

The goal of blob is to provide a simple S3 class to represent a vector of binary objects, aka blobs. The `blob` class is a lightweight wrapper around a list of raw vectors, suitable for inclusion in a data frame.

In most cases you will not need to use this package explicitly: it will be used transparently by packages that need to load BLOB columns from databases or binary file formats.

## Installation

```r
# The easiest way to get blob is to install the whole tidyverse:
install.packages("tidyverse")

# Alternatively, install just blob:
install.packages("blob")

# Or the the development version from GitHub:
# install.packages("pak")
pak::pak("tidyverse/blob")
```

## Example

To create a blob, use `blob()`, `new_blob()` or `as_blob()`:

```{r example}
library(blob)

x1 <- charToRaw("Good morning")
x2 <- as.raw(c(0x48, 0x65, 0x6c, 0x6c, 0x6f))

new_blob(list(x1, x2))
blob(x1, x2)

as_blob(c("Good morning", "Good evening"))
```

---

Please note that the 'blob' project is released with a
[Contributor Code of Conduct](https://github.com/tidyverse/blob/blob/main/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
